\Title

### 2020-03-05 manuscript/manuscript.tex
Remove increment column and include step in values
Ditch the whole Increment columns from parameter tables and include the
increment (step size) into the Values column. Now increment variables
has the following hardcoded text: ", step size " before the actual
numeric interval. This allows to programmatically add steps into the
table without the need to to edit the LaTeX table.

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \GroundGridSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \GroundGridSourcesConstantDepthSpacing
                    & \GroundGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                    & \GroundGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \GroundGridSourcesConstantDepthDamping
                    & \GroundGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \AirborneGridSourcesConstantDepthDepth
                    & \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \AirborneGridSourcesConstantDepthSpacing
                    & \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                    & \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                    & \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

>>>>

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                  \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                  \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                  \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                  \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                  \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                  \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                  \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                  \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                  \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                  \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                  \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                  \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                  \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                  \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                  \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                  \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                  \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                  \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                  \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \GroundGridSourcesConstantDepthDepth
                      \GroundGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \GroundGridSourcesConstantDepthSpacing
                      \GroundGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                     \GroundGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \GroundGridSourcesConstantDepthDamping
                      \GroundGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                  \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                  \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                  \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                  \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                  \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                  \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                  \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                  \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \AirborneGridSourcesConstantDepthDepth
                      \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \AirborneGridSourcesConstantDepthSpacing
                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                      \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                      \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}
